manuscript

### 2022-09-16 ms/manuscript.Rmd
log-transformed mean puzzle

* update supp1 with standard error bars
* update all data by using log-transformed raw data rather than log-transforming means of raw data
  + confusing thing is that the rank order of the raw means is different than the means of the log-transformed data
  + is this correct or did I do something wrong?

```{r}
m <- c(4, 8 , 15, 16, 23, 42)
tmp <- tibble(m, l = log10(x))
tmp_s <- tmp %>% summarize(mean = mean(m), log_mean = mean(l))
tmp_s %<>% mutate(log_m = log(mean))
```

>>>>

* update supp1 with standard error bars
* update all data by using log-transformed raw data rather than log-transforming means of raw data
  + confusing thing is that the rank order of the raw means is different than the means of the log-transformed data
  + is this correct or did I do something wrong?
  + this must be because I am dealing with values smaller than 1 which become negative when log-transformed which can bring down the average
    + hmm I am still getting this result with log1p. not sure what is up

```{r}
m <- c(0.1, 0.5, 4, 8 , 15, 16, 23, 42)
tmp <- tibble(m, l = log10(m))
tmp_s <- tmp %>% summarize(mean = mean(m), log_mean = mean(l))
tmp_s %<>% mutate(log_m = log(mean))
```
